---
title: "README-RegR"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# RegR
Perform basic functions for regression analysis, including scatter plot, linear, lowess, loess, segmented, breakpoint regression. Logarithm transformation is allowed even if variables with 0s by add 1 or 100.

Installation
-----------------
'# Installing just this library (should get all dependancies)
library(devtools) 
install.git_hub("kevinlzheng/RegR")

'# Installing dependancies separately
'# set CRAN mirror 
'#(loads gui in R; in R-Studio select ## of mirror in Console pane)
'# If know mirror can use "ind=" in 2nd statement and comment out (prefix line with #) the first.
chooseCRANmirror()
'#chooseCRANmirror(ind=21)
'################################################
'# must run "chooseCRANmirror()" by itself before running the rest of the script

'# libraries to be installed
data.packages = c(                  
                  "devtools"        # install helper for non CRAN libraries
                  ,"installr"       # install helper
                  ,"digest"         # caused error in R v3.2.3 without it
                  ,"dataRetrieval"  # loads USGS data into R
                  ,"knitr"          # create documents in other formats (e.g., PDF or Word)
                  ,"doBy"           # summary stats
                  ,"zoo"            # z's ordered observations, use for rolling sd calc
                  ,"htmltools"      # needed for knitr and doesn't always install properly with Pandoc
                  ,"rmarkdown"      # needed for knitr and doesn't always install properly with Pandoc
                  ,"htmltools"      # a dependency that is sometimes missed.
                  ,"evaluate"       # a dependency that is sometimes missed.
                  ,"highr"          # a dependency that is sometimes missed.
                  ,"rmarkdown"      # a dependency that is sometimes missed.
                  ,"RColorBrewer"   # for coloring boxplot 
                  )
                  
lapply(data.packages,function(x) install.packages(x))

'## pandoc
require(installr)
install.pandoc()


Purpose
--------------
The scatter plot and multiple regression functions have been used for a long time for various projects. 

Usage
------------
  n = 50
  x <- rlnorm(n) + 1:n
  x <- (x - min(x))/max(x)
  y <- n + 1:n + (rnorm(n))*0.2*n
  scatter.plot(data = data.frame(x,y), xvar= "x", yvar = "y", add.fit = "linear", 
     ylim = range(y), log = "x", x.add = 100, add.r2=T)



